### 2013-07-01 Tex/chapters/results.tex
Angefangen mit conclusion

        \subfigure[][]
        {
            \label{sfig:Tc_norm:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm}
        }
        \subfigure[][]
        {
            \label{sfig:Tc_norm:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm}
        }
        \caption[Critical Temperature over different disorder parameters]
        {
            Top: Critical temperatures over different
            disorder parameters for
            \subref{sfig:Tc:RNG} the Relative Neighborhood Graph and
            \subref{sfig:Tc:GG} the Gabriel Graph.\\
            Middle: Mean sum of the coupling constants to all
            neighbors over different disorder parameters for
            \subref{sfig:sumJ:RNG} the Relative Neighborhood Graph and
            \subref{sfig:sumJ:GG} the Gabriel Graph.\\
            Bottom: Normalized critical temperatures over different
            disorder parameters for
            \subref{sfig:Tc_norm:RNG} the Relative Neighborhood Graph and
            \subref{sfig:Tc_norm:GG} the Gabriel Graph.
        }
        \label{fig:Tc}
    \end{figure}\\
    % I don't know what all that means...
    The Gabriel graph, which is shown on the right side of fig. \ref{fig:Tc},
    jumps from \(\sigma = 0\) to \(\sigma > 0\). This is easily explained
    by the definition of the Gabriel graph and it's aftereffects for
    the transition from \(\sigma = 0\). Visible in fig. \ref{fig:GG_sigma}
    a small change of sigma causes many new egdes to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
    To fully understand this, take four nodes forming a square. The edge
    across does not exist, because the other two nodes are on the edge
    of the lune. Moving one node slightly into the square, causes the lune
    to get smaller, hence no other nodes are inside or on the edge of
    the lune anymore and the edge appears.
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:GG_sigma:zero}
            \includegraphics[width=0.40\textwidth]{images/GG/sigma_e0}
        }
        \subfigure[][]
        {
            \label{sfig:GG_sigma:notzero}
            \includegraphics[width=0.40\textwidth]{images/GG/sigma_g0}
        }
        \caption[Anomaly of the Gabriel graph for small $\sigma$]
        {
            Gabriel graph with periodic boundary conditions for
                \subref{sfig:GG_sigma:zero} \(\sigma = 0\)
                \subref{sfig:GG_sigma:notzero} \(\sigma = 0.01\)
        }
        \label{fig:GG_sigma}
    \end{figure}\\
    Moreover fig. \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}\subref{sfig:Tc_norm:GG}
    shows monotonically decreasing \(T_c\) with increasing disorder
    parameter \(\sigma\). The forms of both curves are similar, but the
    one for the Relative Neighborhood graph \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}
    is generally lower and spans over a bigger temperature range than
    the curve of the Gabriel graph \ref{fig:Tc}\subref{sfig:Tc_norm:GG}.
    % Warum??? Die eigenschaften des Graphen sollten mit der Normalisierung erledigt sein.
    % RNG: laengere Kanten -> weniger lokale effekte?
    For big \(\sigma\) the curve approaches the limit of randomly
    distributed nodes, hence \(T_c\) is independet of \(\sigma\) for
    \(\sigma >> 1\).\\
    Also both graph types have a plateau at \(0 < \sigma < 0.1\). So
    small disorder has little influence on the normalized critical temperature.
    But once the degree of the graph and hence the mean sum of the coupling
    constants decreases, the normalized critical temperature decreases, too.
    % The author is not sure what it means.
    % mit theo ergebnissen von Honeycomb \cite{Wannier1945} vergleichen (fur deg = 3)
    % cosh(2L_c)=2 mit L_c = J/2kT_c -> T_c \approx 1.52

>>>>

        \subfigure[][]
            \label{sfig:Tc_norm:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm}
        \subfigure[][]
            \label{sfig:Tc_norm:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm}
        \caption[Critical Temperature over different disorder parameters]
            Top: Critical temperatures over different
            disorder parameters for
            \subref{sfig:Tc:RNG} the Relative Neighborhood Graph and
            \subref{sfig:Tc:GG} the Gabriel Graph.\\
            Middle: Mean sum of the coupling constants to all
            neighbors over different disorder parameters for
            \subref{sfig:sumJ:RNG} the Relative Neighborhood Graph and
            \subref{sfig:sumJ:GG} the Gabriel Graph.\\
            Bottom: Normalized critical temperatures over different
            disorder parameters for
            \subref{sfig:Tc_norm:RNG} the Relative Neighborhood Graph and
            \subref{sfig:Tc_norm:GG} the Gabriel Graph.
        \label{fig:Tc}
    % I don't know what all that means...
    The Gabriel graph, which is shown on the right side of fig. \ref{fig:Tc},
    jumps from \(\sigma = 0\) to \(\sigma > 0\). This is easily explained
    by the definition of the Gabriel graph and it's aftereffects for
    the transition from \(\sigma = 0\). Visible in fig. \ref{fig:GG_sigma}
    a small change of sigma causes many new egdes to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
    To fully understand this, take four nodes forming a square. The edge
    across does not exist, because the other two nodes are on the edge
    of the lune. Moving one node slightly into the square, causes the lune
    to get smaller, hence no other nodes are inside or on the edge of
    the lune anymore and the edge appears.
        \subfigure[][]
            \label{sfig:GG_sigma:zero}
            \includegraphics[width=0.40\textwidth]{images/GG/sigma_e0}
        \subfigure[][]
            \label{sfig:GG_sigma:notzero}
            \includegraphics[width=0.40\textwidth]{images/GG/sigma_g0}
        \caption[Anomaly of the Gabriel graph for small $\sigma$]
            Gabriel graph with periodic boundary conditions for
                \subref{sfig:GG_sigma:zero} \(\sigma = 0\)
                \subref{sfig:GG_sigma:notzero} \(\sigma = 0.01\)
        \label{fig:GG_sigma}
    Moreover fig. \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}\subref{sfig:Tc_norm:GG}
    shows monotonically decreasing \(T_c\) with increasing disorder
    parameter \(\sigma\). The forms of both curves are similar, but the
    one for the Relative Neighborhood graph \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}
    is generally lower and spans over a bigger temperature range than
    the curve of the Gabriel graph \ref{fig:Tc}\subref{sfig:Tc_norm:GG}.
    % Warum??? Die eigenschaften des Graphen sollten mit der Normalisierung erledigt sein.
    % RNG: laengere Kanten -> weniger lokale effekte?
    For big \(\sigma\) the curve approaches the limit of randomly
    distributed nodes, hence \(T_c\) is independet of \(\sigma\) for
    \(\sigma >> 1\).\\
    Also both graph types have a plateau at \(0 < \sigma < 0.1\). So
    small disorder has little influence on the normalized critical temperature.
    But once the degree -- also called \emph{coordination number} -- of
    the graph and hence the mean sum of the coupling constants decreases,
    the normalized critical temperature decreases, too.\\
    In conclusion the critical temperature depends on the averaged sum
    of the coupling constant \(\avg{\sum_{\avg{i,j}} J_{ij}}\). But after
    normalizing it with this, the plots for both proximity graphs look
    similar.
    % The author is not sure what it means.
    % mit theo ergebnissen von Honeycomb \cite{Wannier1945} vergleichen (fur deg = 3)
    % cosh(2L_c)=2 mit L_c = J/2kT_c -> T_c \approx 1.52
